---
title: "final essay"
author: "B238027"
date: "2024-04-27"
output:
  pdf_document: default
  html_document: default
---

title: "final essay"
author: "B238027"
date: "2024-03-26"
output:
---
#https://cran.r-project.org/web/packages/guardianapi/index.html
#https://github.com/evanodell/guardianapi/tree/master/R


```{r}
library(guardianapi)
```


```{r}
library(tidyverse) # loads dplyr, ggplot2, and others
library(tidytext) # includes set of functions useful for manipulating text
library(ggthemes) # includes a set of themes to make your visualizations look nice!
library(ggplot2) #for visualization
library(readr) # more informative and easy way to import data
library(quanteda) # includes functions to implement Lexicoder
library(quanteda.textstats) # for estimating similarity and complexity measures
library(quanteda.textmodels)
library(stringdist) # for basic character-based distance measures
library(dplyr) #for wrangling data
library(tibble) #for wrangling data
library(tidyverse) # loads dplyr, ggplot2, and others
library(stringr) # to handle text elements
library(topicmodels) # to estimate topic models
library(gutenbergr) # to get text data
library(scales)
library(tm)
library(quanteda.textmodels)
library(lubridate)
library(textdata)
```

#Same-Sex Marriage
#collect data
```{r}
samesexmarrige_2010 <- gu_content(query = "Same-Sex Marriage", from_date = "2010-06-01", to_date = "2010-06-30")
```

```{r}
samesexmarrige_2011 <- gu_content(query = "Same-Sex Marriage", from_date = "2011-06-01", to_date = "2011-06-30")
```

```{r}
samesexmarrige_2012 <- gu_content(query = "Same-Sex Marriage", from_date = "2012-06-01", to_date = "2012-06-30")
```

```{r}
samesexmarrige_2013 <- gu_content(query = "Same-Sex Marriage", from_date = "2013-06-01", to_date = "2013-06-30")
```

```{r}
samesexmarrige_2014 <- gu_content(query = "Same-Sex Marriage", from_date = "2014-06-01", to_date = "2014-06-30")
```

```{r}
samesexmarrige_2015 <- gu_content(query = "Same-Sex Marriage", from_date = "2015-06-01", to_date = "2015-06-30")
```

```{r}
samesexmarrige_2016 <- gu_content(query = "Same-Sex Marriage", from_date = "2016-06-01", to_date = "2016-06-30")
```

```{r}
samesexmarrige_2017 <- gu_content(query = "Same-Sex Marriage", from_date = "2017-06-01", to_date = "2017-06-30")
```

```{r}
samesexmarrige_2018 <- gu_content(query = "Same-Sex Marriage", from_date = "2018-06-01", to_date = "2018-06-30")
```

```{r}
samesexmarrige_2019 <- gu_content(query = "Same-Sex Marriage", from_date = "2019-06-01", to_date = "2019-06-30")
```

```{r}
samesexmarrige_2020 <- gu_content(query = "Same-Sex Marriage", from_date = "2020-06-01", to_date = "2020-06-30")
```

```{r}
head(samesexmarrige_2010)
```
#Save data as CSV file
```{r}
write_csv(samesexmarrige_2010, "/Users/dushijing/Desktop/samesexmarrige_2010.csv")
```

```{r}
write_csv(samesexmarrige_2011, "/Users/dushijing/Desktop/samesexmarrige_2011.csv")
write_csv(samesexmarrige_2012, "/Users/dushijing/Desktop/samesexmarrige_2012.csv")
write_csv(samesexmarrige_2013, "/Users/dushijing/Desktop/samesexmarrige_2013.csv")
write_csv(samesexmarrige_2014, "/Users/dushijing/Desktop/samesexmarrige_2014.csv")
write_csv(samesexmarrige_2015, "/Users/dushijing/Desktop/samesexmarrige_2015.csv")
write_csv(samesexmarrige_2016, "/Users/dushijing/Desktop/samesexmarrige_2016.csv")
write_csv(samesexmarrige_2017, "/Users/dushijing/Desktop/samesexmarrige_2017.csv")
write_csv(samesexmarrige_2018, "/Users/dushijing/Desktop/samesexmarrige_2018.csv")
write_csv(samesexmarrige_2019, "/Users/dushijing/Desktop/samesexmarrige_2019.csv")
write_csv(samesexmarrige_2020, "/Users/dushijing/Desktop/samesexmarrige_2020.csv")
```

#Merge datasets and add year and keyword labels to each dataset
```{r}
#Read the dataset for each year
samesexmarrige_2010 <- read_csv("samesexmarrige_2010.csv")
samesexmarrige_2011 <- read_csv("samesexmarrige_2011.csv")
samesexmarrige_2012 <- read_csv("samesexmarrige_2012.csv")
samesexmarrige_2013 <- read_csv("samesexmarrige_2013.csv")
samesexmarrige_2014 <- read_csv("samesexmarrige_2014.csv")
samesexmarrige_2015 <- read_csv("samesexmarrige_2015.csv")
samesexmarrige_2016 <- read_csv("samesexmarrige_2016.csv")
samesexmarrige_2017 <- read_csv("samesexmarrige_2017.csv")
samesexmarrige_2018 <- read_csv("samesexmarrige_2018.csv")
samesexmarrige_2019 <- read_csv("samesexmarrige_2019.csv")
samesexmarrige_2020 <- read_csv("samesexmarrige_2020.csv")
```
```{r}
#Add keyword columns and year columns to each dataset
samesexmarrige_2010 <- samesexmarrige_2010 %>%
  mutate(keyword = "samesexmarrige", year = 2010)

samesexmarrige_2011 <- samesexmarrige_2011 %>%
  mutate(keyword = "samesexmarrige", year = 2011)

samesexmarrige_2012 <- samesexmarrige_2012 %>%
  mutate(keyword = "samesexmarrige", year = 2012)

samesexmarrige_2013 <- samesexmarrige_2013 %>%
  mutate(keyword = "samesexmarrige", year = 2013)

samesexmarrige_2014 <- samesexmarrige_2014 %>%
  mutate(keyword = "samesexmarrige", year = 2014)

samesexmarrige_2015 <- samesexmarrige_2015 %>%
  mutate(keyword = "samesexmarrige", year = 2015)

samesexmarrige_2016 <- samesexmarrige_2016 %>%
  mutate(keyword = "samesexmarrige", year = 2016)

samesexmarrige_2017 <- samesexmarrige_2017 %>%
  mutate(keyword = "samesexmarrige", year = 2017)

samesexmarrige_2018 <- samesexmarrige_2018 %>%
  mutate(keyword = "samesexmarrige", year = 2018)

samesexmarrige_2019 <- samesexmarrige_2019 %>%
  mutate(keyword = "samesexmarrige", year = 2019)

samesexmarrige_2020 <- samesexmarrige_2020 %>%
  mutate(keyword = "samesexmarrige", year = 2020)

```

```{r}
# Merge data sets for all years
samesexmarrige_data <- bind_rows(samesexmarrige_2010, samesexmarrige_2011, 
                                samesexmarrige_2012,samesexmarrige_2013,samesexmarrige_2014,samesexmarrige_2015,samesexmarrige_2016,samesexmarrige_2017,samesexmarrige_2018,samesexmarrige_2019,samesexmarrige_2020)

# Print column names to confirm columns have been added correctly
names(samesexmarrige_data)
```
```{r}
# See what the existing column names are and how each variable is coded
colnames(samesexmarrige_data)

glimpse(samesexmarrige_data)
```
```{r}
# get simplified dataset with only event contents and year
samesexmarrige_data1 <- samesexmarrige_data %>%
  select(id,web_title,keyword,year)

head(samesexmarrige_data1)
```


#LGBTQ+ Rights
#collect data
```{r}
lgbtqrights_2010 <- gu_content(query = "LGBTQ+ Rights", from_date = "2010-06-01", to_date = "2010-06-30")

```

```{r}
lgbtqrights_2011 <- gu_content(query = "LGBTQ+ Rights", from_date = "2011-06-01", to_date = "2011-06-30")
```

```{r}
lgbtqrights_2012 <- gu_content(query = "LGBTQ+ Rights", from_date = "2012-06-01", to_date = "2012-06-30")
```

```{r}
lgbtqrights_2013 <- gu_content(query = "LGBTQ+ Rights", from_date = "2013-06-01", to_date = "2013-06-30")
```

```{r}
lgbtqrights_2014 <- gu_content(query = "LGBTQ+ Rights", from_date = "2014-06-01", to_date = "2014-06-30")
```

```{r}
lgbtqrights_2015 <- gu_content(query = "LGBTQ+ Rights", from_date = "2015-06-01", to_date = "2015-06-30")
```

```{r}
lgbtqrights_2016 <- gu_content(query = "LGBTQ+ Rights", from_date = "2016-06-01", to_date = "2016-06-30")
```

```{r}
lgbtqrights_2017 <- gu_content(query = "LGBTQ+ Rights", from_date = "2017-06-01", to_date = "2017-06-30")
```

```{r}
lgbtqrights_2018 <- gu_content(query = "LGBTQ+ Rights", from_date = "2018-06-01", to_date = "2018-06-30")
```

```{r}
lgbtqrights_2019 <- gu_content(query = "LGBTQ+ Rights", from_date = "2019-06-01", to_date = "2019-06-30")
```

```{r}
lgbtqrights_2020 <- gu_content(query = "LGBTQ+ Rights", from_date = "2020-06-01", to_date = "2020-06-30")
```

#Save data as CSV file
```{r}
write_csv(lgbtqrights_2010, "/Users/dushijing/Desktop/lgbtqrights_2010.csv")
write_csv(lgbtqrights_2011, "/Users/dushijing/Desktop/lgbtqrights_2011.csv")
write_csv(lgbtqrights_2012, "/Users/dushijing/Desktop/lgbtqrights_2012.csv")
write_csv(lgbtqrights_2013, "/Users/dushijing/Desktop/lgbtqrights_2013.csv")
write_csv(lgbtqrights_2014, "/Users/dushijing/Desktop/lgbtqrights_2014.csv")
write_csv(lgbtqrights_2015, "/Users/dushijing/Desktop/lgbtqrights_2015.csv")
write_csv(lgbtqrights_2016, "/Users/dushijing/Desktop/lgbtqrights_2016.csv")
write_csv(lgbtqrights_2017, "/Users/dushijing/Desktop/lgbtqrights_2017.csv")
write_csv(lgbtqrights_2018, "/Users/dushijing/Desktop/lgbtqrights_2018.csv")
write_csv(lgbtqrights_2019, "/Users/dushijing/Desktop/lgbtqrights_2019.csv")
write_csv(lgbtqrights_2020, "/Users/dushijing/Desktop/lgbtqrights_2020.csv")
```

#Merge datasets and add year and keyword labels to each dataset
```{r}
#Read the dataset for each year
lgbtqrights_2010 <- read_csv("lgbtqrights_2010.csv")
lgbtqrights_2011 <- read_csv("lgbtqrights_2011.csv")
lgbtqrights_2012 <- read_csv("lgbtqrights_2012.csv")
lgbtqrights_2013 <- read_csv("lgbtqrights_2013.csv")
lgbtqrights_2014 <- read_csv("lgbtqrights_2014.csv")
lgbtqrights_2015 <- read_csv("lgbtqrights_2015.csv")
lgbtqrights_2016 <- read_csv("lgbtqrights_2016.csv")
lgbtqrights_2017 <- read_csv("lgbtqrights_2017.csv")
lgbtqrights_2018 <- read_csv("lgbtqrights_2018.csv")
lgbtqrights_2019 <- read_csv("lgbtqrights_2019.csv")
lgbtqrights_2020 <- read_csv("lgbtqrights_2020.csv")
```
```{r}
#Add keyword columns and year columns to each dataset
lgbtqrights_2010 <- lgbtqrights_2010 %>%
  mutate(keyword = "lgbtqrights", year = 2010)

lgbtqrights_2011 <- lgbtqrights_2011 %>%
  mutate(keyword = "lgbtqrights", year = 2011)

lgbtqrights_2012 <- lgbtqrights_2012 %>%
  mutate(keyword = "lgbtqrights", year = 2012)

lgbtqrights_2013 <- lgbtqrights_2013 %>%
  mutate(keyword = "lgbtqrights", year = 2013)

lgbtqrights_2014 <- lgbtqrights_2014 %>%
  mutate(keyword = "lgbtqrights", year = 2014)

lgbtqrights_2015 <- lgbtqrights_2015 %>%
  mutate(keyword = "lgbtqrights", year = 2015)

lgbtqrights_2016 <- lgbtqrights_2016 %>%
  mutate(keyword = "lgbtqrights", year = 2016)

lgbtqrights_2017 <- lgbtqrights_2017 %>%
  mutate(keyword = "lgbtqrights", year = 2017)

lgbtqrights_2018 <- lgbtqrights_2018 %>%
  mutate(keyword = "lgbtqrights", year = 2018)

lgbtqrights_2019 <- lgbtqrights_2019 %>%
  mutate(keyword = "lgbtqrights", year = 2019)

lgbtqrights_2020 <- lgbtqrights_2020 %>%
  mutate(keyword = "lgbtqrights", year = 2020)
```

```{r}
# Merge data sets for all years
lgbtqrights_data <- bind_rows(lgbtqrights_2010,lgbtqrights_2011, 
                            lgbtqrights_2012,lgbtqrights_2013,lgbtqrights_2014,lgbtqrights_2015,lgbtqrights_2016,lgbtqrights_2017,lgbtqrights_2018,lgbtqrights_2019,lgbtqrights_2020)

# Print column names to confirm columns have been added correctly
names(lgbtqrights_data)
```
```{r}
# See what the existing column names are and how each variable is coded
colnames(lgbtqrights_data)

glimpse(lgbtqrights_data)
```

```{r}
# get simplified dataset with only event contents and year
lgbtqrights_data1 <- lgbtqrights_data %>%
  select(id,web_title,keyword,year)

head(lgbtqrights_data1)
```


#marriage equality
#collect data
```{r}
marriageequality_2010 <- gu_content(query = "marriage equality", from_date = "2010-06-01", to_date = "2010-06-30")
```

```{r}
marriageequality_2011 <- gu_content(query = "marriage equality", from_date = "2011-06-01", to_date = "2011-06-30")
```

```{r}
marriageequality_2012 <- gu_content(query = "marriage equality", from_date = "2012-06-01", to_date = "2012-06-30")
```

```{r}
marriageequality_2013 <- gu_content(query = "marriage equality", from_date = "2013-06-01", to_date = "2013-06-30")
```

```{r}
marriageequality_2014 <- gu_content(query = "marriage equality", from_date = "2014-06-01", to_date = "2014-06-30")
```

```{r}
marriageequality_2015 <- gu_content(query = "marriage equality", from_date = "2015-06-01", to_date = "2015-06-30")
```

```{r}
marriageequality_2016 <- gu_content(query = "marriage equality", from_date = "2016-06-01", to_date = "2016-06-30")
```

```{r}
marriageequality_2017 <- gu_content(query = "marriage equality", from_date = "2017-06-01", to_date = "2017-06-30")
```

```{r}
marriageequality_2018 <- gu_content(query = "marriage equality", from_date = "2018-06-01", to_date = "2018-06-30")
```

```{r}
marriageequality_2019 <- gu_content(query = "marriage equality", from_date = "2019-06-01", to_date = "2019-06-30")
```

```{r}
marriageequality_2020 <- gu_content(query = "marriage equality", from_date = "2020-06-01", to_date = "2020-06-30")
```

#Save data as CSV file
```{r}
write_csv(marriageequality_2010, "/Users/dushijing/Desktop/marriageequality_2010.csv")
write_csv(marriageequality_2011, "/Users/dushijing/Desktop/marriageequality_2011.csv")
write_csv(marriageequality_2012, "/Users/dushijing/Desktop/marriageequality_2012.csv")
write_csv(marriageequality_2013, "/Users/dushijing/Desktop/marriageequality_2013.csv")
write_csv(marriageequality_2014, "/Users/dushijing/Desktop/marriageequality_2014.csv")
write_csv(marriageequality_2015, "/Users/dushijing/Desktop/marriageequality_2015.csv")
write_csv(marriageequality_2016, "/Users/dushijing/Desktop/marriageequality_2016.csv")
write_csv(marriageequality_2017, "/Users/dushijing/Desktop/marriageequality_2017.csv")
write_csv(marriageequality_2018, "/Users/dushijing/Desktop/marriageequality_2018.csv")
write_csv(marriageequality_2019, "/Users/dushijing/Desktop/marriageequality_2019.csv")
write_csv(marriageequality_2020, "/Users/dushijing/Desktop/marriageequality_2020.csv")
```

#Merge datasets and add year and keyword labels to each dataset
```{r}
#Read the dataset for each year
marriageequality_2010 <- read_csv("marriageequality_2010.csv")
marriageequality_2011 <- read_csv("marriageequality_2011.csv")
marriageequality_2012 <- read_csv("marriageequality_2012.csv")
marriageequality_2013 <- read_csv("marriageequality_2013.csv")
marriageequality_2014 <- read_csv("marriageequality_2014.csv")
marriageequality_2015 <- read_csv("marriageequality_2015.csv")
marriageequality_2016 <- read_csv("marriageequality_2016.csv")
marriageequality_2017 <- read_csv("marriageequality_2017.csv")
marriageequality_2018 <- read_csv("marriageequality_2018.csv")
marriageequality_2019 <- read_csv("marriageequality_2019.csv")
marriageequality_2020 <- read_csv("marriageequality_2020.csv")
```

```{r}
#Add keyword columns and year columns to each dataset
marriageequality_2010 <- marriageequality_2010 %>%
  mutate(keyword = "marriageequality", year = 2010)

marriageequality_2011 <- marriageequality_2011 %>%
  mutate(keyword = "marriageequality", year = 2011)

marriageequality_2012 <- marriageequality_2012 %>%
  mutate(keyword = "marriageequality", year = 2012)

marriageequality_2013 <- marriageequality_2013 %>%
  mutate(keyword = "marriageequality", year = 2013)

marriageequality_2014 <- marriageequality_2014 %>%
  mutate(keyword = "marriageequality", year = 2014)

marriageequality_2015 <- marriageequality_2015 %>%
  mutate(keyword = "marriageequality", year = 2015)

marriageequality_2016 <- marriageequality_2016 %>%
  mutate(keyword = "marriageequality", year = 2016)

marriageequality_2017 <- marriageequality_2017 %>%
  mutate(keyword = "marriageequality", year = 2017)

marriageequality_2018 <- marriageequality_2018 %>%
  mutate(keyword = "lgbtqrights", year = 2018)

marriageequality_2019 <- marriageequality_2019 %>%
  mutate(keyword = "marriageequality", year = 2019)

marriageequality_2020 <- marriageequality_2020 %>%
  mutate(keyword = "marriageequality", year = 2020)
```

```{r}
# Merge data sets for all years
marriageequality_data <- bind_rows(marriageequality_2010,marriageequality_2011, 
                            marriageequality_2012,marriageequality_2013,marriageequality_2014,marriageequality_2015,marriageequality_2016,marriageequality_2017,marriageequality_2018,marriageequality_2019,marriageequality_2020)

# Print column names to confirm columns have been added correctly
names(marriageequality_data)
```
```{r}
# See what the existing column names are and how each variable is coded
colnames(marriageequality_data)

glimpse(marriageequality_data)
```

```{r}
# get simplified dataset with only event contents and year
marriageequality_data1 <- marriageequality_data %>%
  select(id,web_title,keyword,year)

head(marriageequality_data1)
```


#anti-discrimination
#collect data
```{r}
antidiscrimination_2010 <- gu_content(query = "anti-discrimination", from_date = "2010-06-01", to_date = "2010-06-30")
```

```{r}
antidiscrimination_2011 <- gu_content(query = "anti-discrimination", from_date = "2011-06-01", to_date = "2011-06-30")
```

```{r}
antidiscrimination_2012 <- gu_content(query = "anti-discrimination", from_date = "2012-06-01", to_date = "2012-06-30")
```

```{r}
antidiscrimination_2013<- gu_content(query = "anti-discrimination", from_date = "2013-06-01", to_date = "2013-06-30")
```

```{r}
antidiscrimination_2014<- gu_content(query = "anti-discrimination", from_date = "2014-06-01", to_date = "2014-06-30")
```

```{r}
antidiscrimination_2015<- gu_content(query = "anti-discrimination", from_date = "2015-06-01", to_date = "2015-06-30")
```

```{r}
antidiscrimination_2016<- gu_content(query = "anti-discrimination", from_date = "2016-06-01", to_date = "2016-06-30")
```

```{r}
antidiscrimination_2017<- gu_content(query = "anti-discrimination", from_date = "2017-06-01", to_date = "2017-06-30")
```

```{r}
antidiscrimination_2018<- gu_content(query = "anti-discrimination", from_date = "2018-06-01", to_date = "2018-06-30")
```

```{r}
antidiscrimination_2019<- gu_content(query = "anti-discrimination", from_date = "2019-06-01", to_date = "2019-06-30")
```

```{r}
antidiscrimination_2020<- gu_content(query = "anti-discrimination", from_date = "2020-06-01", to_date = "2020-06-30")
```

#Save data as CSV file
```{r}
write_csv(antidiscrimination_2010, "/Users/dushijing/Desktop/antidiscrimination_2010.csv")
write_csv(antidiscrimination_2011, "/Users/dushijing/Desktop/antidiscrimination_2011.csv")
write_csv(antidiscrimination_2012, "/Users/dushijing/Desktop/antidiscrimination_2012.csv")
write_csv(antidiscrimination_2013, "/Users/dushijing/Desktop/antidiscrimination_2013.csv")
write_csv(antidiscrimination_2014, "/Users/dushijing/Desktop/antidiscrimination_2014.csv")
write_csv(antidiscrimination_2015, "/Users/dushijing/Desktop/antidiscrimination_2015.csv")
write_csv(antidiscrimination_2016, "/Users/dushijing/Desktop/antidiscrimination_2016.csv")
write_csv(antidiscrimination_2017, "/Users/dushijing/Desktop/antidiscrimination_2017.csv")
write_csv(antidiscrimination_2018, "/Users/dushijing/Desktop/antidiscrimination_2018.csv")
write_csv(antidiscrimination_2019, "/Users/dushijing/Desktop/antidiscrimination_2019.csv")
write_csv(antidiscrimination_2020, "/Users/dushijing/Desktop/antidiscrimination_2020.csv")
```

#Merge datasets and add year and keyword labels to each dataset
```{r}
#Read the dataset for each year
antidiscrimination_2010 <- read_csv("antidiscrimination_2010.csv")
antidiscrimination_2011 <- read_csv("antidiscrimination_2011.csv")
antidiscrimination_2012 <- read_csv("antidiscrimination_2012.csv")
antidiscrimination_2013 <- read_csv("antidiscrimination_2013.csv")
antidiscrimination_2014 <- read_csv("antidiscrimination_2014.csv")
antidiscrimination_2015 <- read_csv("antidiscrimination_2015.csv")
antidiscrimination_2016 <- read_csv("antidiscrimination_2016.csv")
antidiscrimination_2017 <- read_csv("antidiscrimination_2017.csv")
antidiscrimination_2018 <- read_csv("antidiscrimination_2018.csv")
antidiscrimination_2019 <- read_csv("antidiscrimination_2019.csv")
antidiscrimination_2020 <- read_csv("antidiscrimination_2020.csv")
```

```{r}
#Add keyword columns and year columns to each dataset
antidiscrimination_2010 <- antidiscrimination_2010 %>%
  mutate(keyword = "antidiscrimination", year = 2010)

antidiscrimination_2011 <- antidiscrimination_2011 %>%
  mutate(keyword = "antidiscrimination", year = 2011)

antidiscrimination_2012 <- antidiscrimination_2012 %>%
  mutate(keyword = "antidiscrimination", year = 2012)

antidiscrimination_2013 <- antidiscrimination_2013 %>%
  mutate(keyword = "antidiscrimination", year = 2013)

antidiscrimination_2014 <- antidiscrimination_2014 %>%
  mutate(keyword = "antidiscrimination", year = 2014)

antidiscrimination_2015 <- antidiscrimination_2015 %>%
  mutate(keyword = "antidiscrimination", year = 2015)

antidiscrimination_2016 <- antidiscrimination_2016 %>%
  mutate(keyword = "antidiscrimination", year = 2016)

antidiscrimination_2017 <- antidiscrimination_2017 %>%
  mutate(keyword = "antidiscrimination", year = 2017)

antidiscrimination_2018 <- antidiscrimination_2018 %>%
  mutate(keyword = "antidiscrimination", year = 2018)

antidiscrimination_2019 <- antidiscrimination_2019 %>%
  mutate(keyword = "antidiscrimination", year = 2019)

antidiscrimination_2020 <- antidiscrimination_2020 %>%
  mutate(keyword = "antidiscrimination", year = 2020)
```

```{r}
# Merge data sets for all years
antidiscrimination_data <- bind_rows(antidiscrimination_2010,antidiscrimination_2011, 
                            antidiscrimination_2012,antidiscrimination_2013,antidiscrimination_2014,antidiscrimination_2015,antidiscrimination_2016,antidiscrimination_2017,antidiscrimination_2018,antidiscrimination_2019,antidiscrimination_2020)

# Print column names to confirm columns have been added correctly
names(antidiscrimination_data)
```
```{r}
# See what the existing column names are and how each variable is coded
colnames(antidiscrimination_data)

glimpse(antidiscrimination_data)
```

```{r}
# get simplified dataset with only event contents and year
antidiscrimination_data1 <- antidiscrimination_data %>%
  select(id,web_title,keyword,year)

head(antidiscrimination_data1)
```


#legal protection
#collect data
```{r}
legalprotection_2010 <- gu_content(query = "legal protection", from_date = "2010-06-01", to_date = "2010-06-30")
```

```{r}
legalprotection_2011 <- gu_content(query = "legal protection", from_date = "2011-06-01", to_date = "2011-06-30")
```

```{r}
legalprotection_2012 <- gu_content(query = "legal protection", from_date = "2012-06-01", to_date = "2012-06-30")
```

```{r}
legalprotection_2013 <- gu_content(query = "legal protection", from_date = "2013-06-01", to_date = "2013-06-30")
```

```{r}
legalprotection_2014 <- gu_content(query = "legal protection", from_date = "2014-06-01", to_date = "2014-06-30")
```

```{r}
legalprotection_2015 <- gu_content(query = "legal protection", from_date = "2015-06-01", to_date = "2015-06-30")
```

```{r}
legalprotection_2016 <- gu_content(query = "legal protection", from_date = "2016-06-01", to_date = "2016-06-30")
```

```{r}
legalprotection_2017 <- gu_content(query = "legal protection", from_date = "2017-06-01", to_date = "2017-06-30")
```

```{r}
legalprotection_2018 <- gu_content(query = "legal protection", from_date = "2018-06-01", to_date = "2018-06-30")
```

```{r}
legalprotection_2019 <- gu_content(query = "legal protection", from_date = "2019-06-01", to_date = "2019-06-30")
```

```{r}
legalprotection_2020 <- gu_content(query = "legal protection", from_date = "2020-06-01", to_date = "2020-06-30")
```


```{r}
#Save data as CSV file
write_csv(legalprotection_2010, "/Users/dushijing/Desktop/legalprotection_2010.csv")
write_csv(legalprotection_2011, "/Users/dushijing/Desktop/legalprotection_2011.csv")
write_csv(legalprotection_2012, "/Users/dushijing/Desktop/legalprotection_2012.csv")
write_csv(legalprotection_2013, "/Users/dushijing/Desktop/legalprotection_2013.csv")
write_csv(legalprotection_2014, "/Users/dushijing/Desktop/legalprotection_2014.csv")
write_csv(legalprotection_2015, "/Users/dushijing/Desktop/legalprotection_2015.csv")
write_csv(legalprotection_2016, "/Users/dushijing/Desktop/legalprotection_2016.csv")
write_csv(legalprotection_2017, "/Users/dushijing/Desktop/legalprotection_2017.csv")
write_csv(legalprotection_2018, "/Users/dushijing/Desktop/legalprotection_2018.csv")
write_csv(legalprotection_2019, "/Users/dushijing/Desktop/legalprotection_2019.csv")
write_csv(legalprotection_2020, "/Users/dushijing/Desktop/legalprotection_2020.csv")
```

#Merge datasets and add year and keyword labels to each dataset
```{r}
#Read the dataset for each year
legalprotection_2010 <- read_csv("legalprotection_2010.csv")
legalprotection_2011 <- read_csv("legalprotection_2011.csv")
legalprotection_2012 <- read_csv("legalprotection_2012.csv")
legalprotection_2013 <- read_csv("legalprotection_2013.csv")
legalprotection_2014 <- read_csv("legalprotection_2014.csv")
legalprotection_2015 <- read_csv("legalprotection_2015.csv")
legalprotection_2016 <- read_csv("legalprotection_2016.csv")
legalprotection_2017 <- read_csv("legalprotection_2017.csv")
legalprotection_2018 <- read_csv("legalprotection_2018.csv")
legalprotection_2019 <- read_csv("legalprotection_2019.csv")
legalprotection_2020 <- read_csv("legalprotection_2020.csv")
```

```{r}
#Add keyword columns and year columns to each dataset
legalprotection_2010 <- legalprotection_2010 %>%
  mutate(keyword = "legalprotection", year = 2010)

legalprotection_2011 <- legalprotection_2011 %>%
  mutate(keyword = "legalprotection", year = 2011)

legalprotection_2012 <- legalprotection_2012 %>%
  mutate(keyword = "legalprotection", year = 2012)

legalprotection_2013 <- legalprotection_2013 %>%
  mutate(keyword = "legalprotection", year = 2013)

legalprotection_2014 <- legalprotection_2014 %>%
  mutate(keyword = "legalprotection", year = 2014)

legalprotection_2015 <- legalprotection_2015 %>%
  mutate(keyword = "legalprotection", year = 2015)

legalprotection_2016 <- legalprotection_2016 %>%
  mutate(keyword = "legalprotection", year = 2016)

legalprotection_2017 <- legalprotection_2017 %>%
  mutate(keyword = "legalprotection", year = 2017)

legalprotection_2018 <- legalprotection_2018 %>%
  mutate(keyword = "legalprotection", year = 2018)

legalprotection_2019 <- legalprotection_2019 %>%
  mutate(keyword = "legalprotection", year = 2019)

legalprotection_2020 <- legalprotection_2020 %>%
  mutate(keyword = "legalprotection", year = 2020)
```

```{r}
# Merge data sets for all years
legalprotection_data <- bind_rows(legalprotection_2010,legalprotection_2011, 
                            legalprotection_2012,legalprotection_2013,legalprotection_2014,legalprotection_2015,legalprotection_2016,legalprotection_2017,legalprotection_2018,legalprotection_2019,legalprotection_2020)

# Print column names to confirm columns have been added correctly
names(legalprotection_data)
```

```{r}
# See what the existing column names are and how each variable is coded
colnames(legalprotection_data)

glimpse(legalprotection_data)
```

```{r}
# get simplified dataset with only event contents and year
legalprotection_data1 <- legalprotection_data %>%
  select(id,web_title,keyword,year)

head(legalprotection_data1)
```

```{r}
# Merge data sets for all keyword dataset
all_data <- bind_rows(samesexmarrige_data1,lgbtqrights_data1,marriageequality_data1,antidiscrimination_data1,legalprotection_data1)

# Print column names to confirm columns have been added correctly
names(all_data)
```

```{r}
#A quick look at the number of news stories mentioning LGBTQ+ related news between 2010-2020.
all_datayr <- all_data %>%
  mutate(obs=1) %>%
  group_by(year) %>%
  summarise(sum_coverage = sum(obs))

ggplot(all_datayr) +
  geom_line(aes(year, sum_coverage)) +
  theme_tufte(base_family = "Helvetica") + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA))
```

```{r}
clean_all_data <- all_data %>%
  # Convert titles to lower case
  mutate(web_title = tolower(web_title)) %>%
  # Create bigrams
  unnest_tokens(bigram, web_title, token = "ngrams", n = 2) %>%
  # Split bigrams into two separate words
  separate(bigram, into = c("word1", "word2"), sep = " ")

# Removing bigrams containing stop words
clean_all_data <- clean_all_data %>%
  filter(!(word1 %in% stop_words$word | word2 %in% stop_words$word)) %>%
  
  # Make sure each word contains only letters
  filter(str_detect(word1, "^[a-z]+$") & str_detect(word2, "^[a-z]+$"))

# Remove remaining special characters
remove_reg <- c("&amp;", "&lt;", "&gt;", "<p>", "</p>", "&rsquo;", "&lsquo;", 
                "&#39;", "<strong>", "</strong>", "rsquo", "em", "ndash", "nbsp", 
                "lsquo", "strong")
clean_all_data <- clean_all_data %>%
  filter(!word1 %in% remove_reg & !word2 %in% remove_reg)

clean_all_data %>%
  unite(bigram, word1, word2, sep = " ") %>%
count(bigram,sort = TRUE)
```
```{r}
clean_all_data <- clean_all_data %>%
  unite("bigram", word1, word2, sep = " ")

# Calculate the frequency of bigrams
clean_all_data_bigram_term_counts <- clean_all_data %>%
  group_by(year, keyword, bigram) %>%
  count(bigram, sort = TRUE)

# View the most common bigrams
head(clean_all_data_bigram_term_counts)
```

```{r}
bigram_counts <- clean_all_data %>%
  count(bigram, sort = TRUE)

head(bigram_counts)
```

```{r}
# Modify the dataset to add new columns to mark headings that contain specific supporting keywords

clean_all_data_bigram_term_counts$supportive_word <- as.integer(grepl(
  "gay marriage|sex marriage|legal aid|human rights|supreme court|\
   civil rights|gender equality|sexual orientation|gender identity rights|\
   pride support|equality champion|rights advocacy|protection laws|\
   social justice|equality parade|LGBTQ inclusion|\
   UK Parliament|British law|Equality Act|UK Supreme Court|Brexit impact|\
   England|Scotland|Wales|Northern Ireland|Scotland legislation|\
   Wales rights|Northern Ireland equality|House of Lords decisions|\
   House of Commons debates",
  x = clean_all_data_bigram_term_counts$bigram, ignore.case = TRUE
))


head(clean_all_data_bigram_term_counts)
```
```{r}
#get counts by year and word
all_data_lgbtq_counts <- clean_all_data_bigram_term_counts %>%
  group_by(year) %>%
  mutate(year_total = sum(n)) %>%
  filter(supportive_word==1) %>%
  summarise(sum_sup = sum(n),
            year_total= min(year_total))
head(all_data_lgbtq_counts)
```
```{r}
#Count the number of LGBTQ+ supportive-related words in that dataset and name them based on the total number of words in those data for each year

ggplot(all_data_lgbtq_counts, aes(year, sum_sup / year_total, group=1)) +
  geom_line() +
  xlab("Year") +
  ylab("% lgbtqsupportive-related words") +
  scale_y_continuous(labels = scales::percent_format(),
                     expand = c(0, 0), limits = c(0, NA)) +
  theme_tufte(base_family = "Helvetica") 
```

```{r}
#Tagged 2014 is the year same-sex marriage is legalised in England, Wales, Scotland

ggplot(all_data_lgbtq_counts, aes(year, sum_sup / year_total, group=1)) +
  geom_line() +
  geom_vline(xintercept = 2014, col="red") +
  geom_text(aes(x=2014, label="#englandwalesscotland year", y=.0015), 
            colour="black", angle=90, text=element_text(size=8)) +
  xlab("Year") +
  ylab("% lgbtqsupportive-related words") +
  scale_y_continuous(labels = scales::percent_format(),
                     expand = c(0, 0), limits = c(0, NA)) +
  theme_tufte(base_family = "Helvetica")
```

#Using Lexicoder
```{r}
# Create a corpus 
# Make sure the year column is in date format
clean_all_data$year <- as.Date(as.character(clean_all_data$year), format="%Y")

# Creating corpus objects
all_data_corpus <- corpus(clean_all_data, text_field = "bigram", docvars = c("id", "keyword", "year"))

#Use the functions in quanteda to tag the text tokens() and remove punctuation marks
tok_news <- tokens(all_data_corpus, remove_punct = TRUE)
```

#Bundle data_dictionary_LSD2015 with and quanteda and select only positive and negative categories, excluding words considered "neutral". 
# "Look up" in this dictionary how to use the tokens_lookup() function to rate tokens in the corpus.
```{r}
# select only the "negative" and "positive" categories
data_dictionary_LSD2015_pos_neg <- data_dictionary_LSD2015[1:2]

tok_news_lsd <- tokens_lookup(tok_news, dictionary = data_dictionary_LSD2015_pos_neg)
```

```{r}
# create a document document-feature matrix and group it by year
dfmat_news_lsd <- dfm(tok_news_lsd) %>% 
  dfm_group(groups = year)

# plot positive and negative valence over time
matplot(dfmat_news_lsd$year, dfmat_news_lsd, type = "l", lty = 1, col = 1:2,
        ylab = "Frequency", xlab = "")
grid()
legend("topleft", col = 1:2, legend = colnames(dfmat_news_lsd), lty = 1, bg = "white")
```

```{r}
# plot overall sentiment (positive  - negative) over time

plot(dfmat_news_lsd$year, dfmat_news_lsd[,"positive"] - dfmat_news_lsd[,"negative"], 
     type = "l", ylab = "Sentiment", xlab = "")
grid()
abline(h = 0, lty = 2)
```


